Aldebaran~b's temperate past uncovered in planet search data

### 2018-02-25 paper/aldebaran.tex
As submitted.
autograd

In an improvement since \citet{White2017}, we use the \textsc{Theano} library \citep{theano} to calculate analytic derivatives for the TV objective function, which reduces the computational time for a single halo light curve on a commercial laptop from tens of minutes to tens of seconds.

>>>>

In an improvement since \citet{White2017}, we use the \textsc{autograd} library \citep{maclaurinautograd} to calculate analytic derivatives for the TV objective function, which reduces the computational time for a single halo light curve on a commercial laptop from tens of minutes to a few seconds.
